---
output:
  github_document:
    html_preview: false
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
library(ggplot2)
```


## Overview

`"binomial"` allows the user to experiment with different calculations and visualizations of a binomial random variable.

* `bin_var()` creates a binomial random variable object (of class `"bin_var"`)
* `bin_distribution()` produces a `"bindis"` object that displays the density of the binomial random variable in table format.
* `bin_cumulative()` produces a `"bincum"` object that displays the cumulative binomial distribution in table format.
* `plot()` method for a `"bindis"` and `"bincum"` object.
* `summary()` method for a `"bin_var"` object.
* `bin_mean()`, `bin_variance()`, `bin_mode()`, `bin_skewness()`, `bin_kurtosis()` for specific statistics.
* `bin_probability()` for density function of binomial random variable.
* `bin_choose()` for the binomial coefficient.


## Motivation

This package has been developed as an exercise for creating a simple R package.

## Usage

```{r}
library(binomial)
#binomial random variable
bin_var <- bin_variable(trials = 5, prob = 0.5)
print(bin_var)
# show summary
summary(bin_var)
# summary statistics
bin_mean(trials = 5, prob = 0.5)
bin_variance(trials = 5, prob = 0.5)
bin_mode(trials = 5, prob = 0.5)
bin_skewness(trials = 5, prob = 0.5)
bin_kurtosis(trials = 5, prob = 0.5)
# density function
bin_probability(success = 2, trials = 5, prob = 0.5)
# binomial coefficient
bin_choose(n = 5, k = 2)
# Tables of density and cumulative binomial distribution
bin_dis <- bin_distribution(trials = 5, prob = 0.5)
bin_dis
bin_cum <- bin_cumulative(trials = 5, prob = 0.5)
bin_cum
#Plots of density and cumulative binomial distribution
plot(bin_dis)
plot(bin_cum)