---
title: "Getting Started with binomial"
author: "Warren Gu"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to binomial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(binomial)
library(ggplot2)
```

## Binomial

The package `"binomial"` allows the user to experiment with different calculations and visualizations of a binomial random variable.


## Creating a `bin_var`

The first step is to create a `"bin_var"` object with the function `bin_variable()` which takes in two arguments: `trials` and `prob`:

```{r}
bin_var <- bin_variable(trials = 5, prob = 0.5)
print(bin_var)
```

`bin_var` now has the distribution Binom(`trials`, `prob`):

## Summary statistics

Now that we have a `bin_var` object, we can view the different summary statistics of `bin_var`.

```{r}
summary(bin_var)
```

Here, we see that we can view the mean, variance, mode, skewness, and kurtosis of `bin_var`. If we would like to only view one specific statistic, we also have a function for each statistic.

```{r}
bin_mean(trials = 5, prob = 0.5)
bin_variance(trials = 5, prob = 0.5)
bin_mode(trials = 5, prob = 0.5)
bin_skewness(trials = 5, prob = 0.5)
bin_kurtosis(trials = 5, prob = 0.5)
```

## Density function

To calculate the binomial random variable's density at a specific success, you can use the `bin_probability()` function.

```{r}
bin_probability(success = 2, trials = 5, prob = 0.5)
```

You can also calculate the binomial coefficient using the `bin_choose()` function.

```{r}
bin_choose(n = 5, k = 2)
```


## Tables and Plots

You can use the function `bin_distribution()` to create tables of the binomial probability distribution and the cumulative binomial distribution respectively.

```{r, fig.show='hold'}
bin_dis <- bin_distribution(trials = 5, prob = 0.5)
bin_dis
```

To visualize the probability distribution, use the `plot()` function.

```{r}
plot(bin_dis)
```

You can also use the function `bin_cumulative()` to create a table of the cumulative binomial probability distribution.

```{r, fig.show='hold'}
bin_cum <- bin_cumulative(trials = 5, prob = 0.5)
bin_cum
```

Similarly, you can visualize the probability distribution using the `plot()` function.

```{r}
plot(bin_cum)
```
